NFC and burnout in teachers - A replication and extension study

### 2021-10-27 Manuscript/Manuscript.Rmd
created plot for exploratory analysis

@@

  fit_explor2_param <- fit_explor2_summ$PE$std.all[c(1:10,16:32)]
  fit_explor2_sign <- c(rep(1,10), fit_explor2_summ$PE$pvalue[16:32])

@@

  fit_explor2_plot <- semPaths(fit_explor2, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4",
                                       "dth1","dth2","dth3","drf1","drf2","drf3",
                                       "YEARS",
                                       "SCS",
                                       "COVB",
                                       "NFC",
                                       "DRF","DTH",
                                       "MBI_EE","MBI_RPE"),
                        layout = matrix(data = c(-0.7,-0.56,-0.44,-0.3,
                                                 0.3,0.5,0.7,0.3,0.5,0.7,
                                                 -1,
                                                 -0.4,
                                                 -0.4,
                                                 -0.4,
                                                 0.4,0.4,
                                                 1,1,
                                                 1,1,1,1,
                                                 1,1,1,-1,-1,-1,
                                                 -0.3,
                                                 -1,
                                                 -0.3,
                                                 0.5,
                                                 0.5,-0.5,
                                                 0.5,-0.5),
                                        nrow = 18, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edgeLabels = fit_explor2_param, # specify the edge labels with the asterisks as previously created
                        edge.label.cex = 1, esize = 2, # size of the parameters
                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
                        posCol = "black", negCol = "black" # color of arrows
  )
```

>>>>

    MBI_EE ~~ MBI_RPE
    NFC ~~ YEARS

@@

  fit_explor2_param <- fit_explor2_summ$PE$std.all[c(1:30)]
  fit_explor2_sign <- c(rep(1,15), fit_explor2_summ$PE$pvalue[16:30])

@@

  fit_explor2_plot <- semPaths(fit_explor2, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4",
                                       "dth1","dth2","dth3","drf1","drf2","drf3",
                                       "mbi_ee", "mbi_rpe",
                                       "scs", "covb", "years",
                                       "NFC",
                                       "DTH","DRF",
                                       "MBI_EE","MBI_RPE",
                                       "SCS",
                                       "COVB",
                                       "YEARS"),
                        layout = matrix(data = c(-0.6,-0.4,-0.2,0,
                                                 0.3,0.5,0.7,0.3,0.5,0.7,
                                                 1,1,
                                                 -0.5,-0.2,-1,
                                                 -0.2,
                                                 0.5,0.5,
                                                 1,1,
                                                 -0.5,
                                                 -0.2,
                                                 -1,
                                                 1,1,1,1,
                                                 -1,-1,-1,1,1,1,
                                                 -1,1,
                                                 -1,-1,-1,
                                                 0.5,
                                                 -0.5,0.5,
                                                 0,0.5,
                                                 0.1,
                                                 -0.4,
                                                 0.1),
                                        nrow = 23, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edgeLabels = fit_explor2_param, # specify the edge labels with the asterisks as previously created
                        edge.label.cex = 1, esize = 2, # size of the parameters
                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
                        posCol = "black", negCol = "black" # color of arrows
  )
```
